What We Eval in the Shadows

### 2021-04-16 paper/main.tex
Side effects: numbers to compare with javascript

\paragraph{Discussion}
The origin data suggests that constructing expressions from strings is a
minority of the use cases. Instead, the constructed category shows that most \evals comes from code that was processed by the compiler, and may be
slightly modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those.

@@

\mypara{Discussion} In JavaScript assignments in \eval can happen in either
local scope or less often, when called through an alias, in the global scope.
In R, given the support for first-class environments, it can happen anywhere, 
making it \eval more dangerous than it already is. However, the data  suggest
that first, side-effects from \eval are not as widespread as in the case of
JavaScript and that over half of them happen in a predictable environment.

>>>>

\paragraph{Discussion}

% Compare to JS ? Everything comes from a string in JS anyway
% Composite (concatenation of strings), DOM and constant are the most common
% ...
The origin data suggests that constructing expressions from strings is a
minority of the use cases. Instead, the constructed category shows that most \evals comes from code that was processed by the compiler, and may be
slightly modified by the programmer before invoking \eval. Both constructed and
reflection categories roughly correspond to meta-programming. Some of these use
cases could likely be replaced by macros if the R designers could be convinced
to overcome their distaste for those.

@@

\mypara{Discussion} In JavaScript assignments in \eval can happen in either
local scope or less often, when called through an alias, in the global scope.
In R, given the support for first-class environments, it can happen anywhere, 
making it \eval more dangerous than it already is. However, the data  suggest
that first, side-effects from \eval are not as widespread as in the case of
JavaScript, \footnote{\citep{ecoop11} shows that in the \emph{Interactive} scenario, \eval in Javascript performs, store events can reach up to 40\% of the events, and 7\% to 8\% of the \eval do side effects in the global scope. } and that over half of them happen in a predictable environment.
